---
title: "Portfolios 5"
author: "Qilin Zhang"
date: "2023-04-20"
output: html_document
---

##Multigroup Analysis

This is an example of a multigroup analysis that I did recently to test the measurement invariance of a morality scale across Chinese and US samples. Since this is mostly just running different model so that output looks very similar. I do find the table for comparing fit indexes very helpful at the end. 


```{r pac, message = FALSE, include=FALSE}
library(summarytools)
library(tidyverse) #data wrangling
library(codebook) #codebook generation
library(future) #reliability
library(ufs) #reliability
library(GGally) #reliability
library(GPArotation) #reliability
library(rio) #reading in different file types
library(labelled) #labeling data
library(psych)
library(corrplot) 
library(psych)
library(mirt)
library(eRm)
library(mice)
library(lavaan)
library(semPlot)
library(parameters)
library(broom)
library(likert)
library(sjPlot)
library(readxl)
library(foreign)
library(lme4)
library(lmerTest)
library(mvnormtest)
library(mvnormalTest)
library(ggpubr)
library(rstatix)
library(heplots)
library(knitr)
library(MOTE)
```

### cleaning
```{r import, include = FALSE}

## use other read functions as appropriate for file type

dict <- read_excel("Data/CLS_dictionary.xlsx") #dictionary

data <- read_excel("Data/CLS_cleaned.xlsx") #data

#prepare the data just for MCQ analysis

MCQ_CN <- data[,c(grep("MCQ_1$",colnames(data)):grep("MCQ_30",colnames(data)))]

## Variable types

names <- dict %>% 
  filter(type == "numeric") %>% 
  pull(variable)
data[,names] <- 
  lapply(data[,names], as.numeric)

rm(names)
```

```{r missing, include = FALSE}
#function for checking percentage of missing data (unit=%)
percent_missing <- function(x){
  sum(is.na((x))/length(x)*100)
}
missing_R <- apply(MCQ_CN,1,percent_missing)
table(missing_R)

#check where the NAs are if needed
rindex <- rep(FALSE, nrow(MCQ_CN))
for (i in 1:nrow(MCQ_CN)){
  for (j in 1:grep("MCQ_30",colnames(MCQ_CN))){
    if( is.na(MCQ_CN[i,j])){
      rindex[i] = TRUE
      j = ncol(MCQ_CN)+1
    }
  }
}
data_error <- MCQ_CN[rindex,]

rm(data_error)

#use if don't want imputation(turn off if I need imputation)
MCQ_CN <- subset(MCQ_CN, missing_R<=0)


##remove people that gave 90% of the same answer in MCQ

for(i in 1:5){
  percent <- function(x){
  sum((x == i)/length(x)*100)
  }
  number <- apply(MCQ_CN,1,percent)
  MCQ_CN <- MCQ_CN[c(number<90),]
}
```

###assumption
``` {R assumption, include = FALSE}
## assumption check
random_variable <- rchisq(nrow(MCQ_CN), 7)# use Chi-square here because error terms are likely chi-sqaure distributed
fake_model <- lm(random_variable ~ ., 
                 MCQ_CN) # prediction here should be random because the error is randomized
standardized <- rstudent(fake_model) # standardize error terms
fitvalues <- scale(fake_model$fitted.values)
plot(fake_model,2)#check for linearity
#We assume the multivariate relationship between continuous variables is linear (i.e., no curved)
#There are many ways to test this, but we can use a QQ/PP Plot to examine for linearity

hist(standardized)#check for normality
#We expect that the residuals are normally distributed (centered at 0 and most of the data between -2 - 2)
#Not that the *sample* is normally distributed 
#Generally, SEM requires a large sample size, thus, buffering against normality deviations

{plot(standardized, fitvalues)
  abline(v = 0)
  abline(h = 0)
}#check for homogeneity + Homoscedasticity
#These assumptions are about equality of the variances
#We assume equal variances between groups for things like t-tests, ANOVA
#Here the assumption is equality in the spread of variance across predicted values 


#assumption about correlation
cor_matrix <- 
  MCQ_CN%>%
  cor() # check correlation between two variables

cor_matrix

corrplot(cor_matrix)

cortest.bartlett(cor_matrix, n = nrow(MCQ_CN))


#multivariate normality
mardia(MCQ_CN)
mshapiro_test(MCQ_CN)
```

####Multi group models

```{r include=FALSE}
#import
library(haven)

MCQ_US <- read_sav("//10.4.6.5/psychology/labs/beaconproject/Empirical Research Activities/Study 1-Do Self-Identified ME Differ/The 10000/Data/Data for Analysis (CLEAN)/The 10000_Data Downloaded FOR ANALYSIS.sav")


#retain only items relating to MCQ
MCQ_US <- MCQ_US %>%
  select(c(starts_with("MTS")))

MCQ_US <- MCQ_US[,-c(35:45)] %>% 
  select(!contains("Hum"))

```

```{r clean}

#clean missing data
missing_R <- apply(MCQ_US,1,percent_missing)
table(missing_R)

MCQ_US <- subset(MCQ_US, missing_R<=0)

#rename to match the CN dataset
names(MCQ_US) <- c("MCQ_1","MCQ_2","MCQ_3","MCQ_4","MCQ_5","MCQ_6",
                   "MCQ_19","MCQ_20","MCQ_21","MCQ_22",
                   "MCQ_7","MCQ_8","MCQ_9","MCQ_10",
                   "MCQ_15","MCQ_16","MCQ_17","MCQ_18",
                   "MCQ_11","MCQ_12","MCQ_13","MCQ_14",
                   "MCQ_23","MCQ_24","MCQ_25","MCQ_26",
                   "MCQ_27","MCQ_28","MCQ_29","MCQ_30")
```


```{r}
#data binding and summary stat
MCQ_CN$country <- rep(1, nrow(MCQ_CN))

MCQ_US$country <- rep(2, nrow(MCQ_US))

MCQ <- rbind.data.frame(MCQ_CN,MCQ_US)

table(MCQ$country) #343 Chinese participants and 9365 American

MCQ$country <- factor(MCQ$country,
                      levels = c(1,2),
                      labels = c("Chinese","American"))
```

#General model

```{r}

overall.model <- '
GM =~ MCQ_1 + MCQ_2 + MCQ_3 + MCQ_4 + MCQ_5 + MCQ_6 + H + C + F + L + P + R 
H =~ MCQ_7 + MCQ_8 + MCQ_9 + MCQ_10 
C =~ MCQ_11 + MCQ_12 + MCQ_13 + MCQ_14 
F =~ MCQ_15 + MCQ_16 + MCQ_17 + MCQ_18 
L =~ MCQ_19 + MCQ_20 + MCQ_21 + MCQ_22 
P =~ MCQ_23 + MCQ_24 + MCQ_25 + MCQ_26 
R =~ MCQ_27 + MCQ_28 + MCQ_29 + MCQ_30 
RC =~ MCQ_2 + MCQ_7 + MCQ_14 + MCQ_17 + MCQ_20 + MCQ_25 + MCQ_28
'
overall.fit <- cfa(model = overall.model,
                   data = MCQ,
                   meanstructure = TRUE)

summary(overall.fit,
        standardized = T,
        rsquare = T,
        fit.measures = T)


table_fit <- matrix(NA,nrow = 7, ncol = 6)
colnames(table_fit)<- c("model","X2","df","CFI","RMSEA","SRMR")
table_fit[1,] <- c("Overall Model", round(fitmeasures(overall.fit,c("chisq","df","cfi","rmsea","srmr")),3))
kable(table_fit)

semPaths(overall.fit,
         whatLabels = "std",
         edge.label.cex = 1,
         layout = "tree")
```


```{r}
#American sample alone
American.model <- '
GM =~ MCQ_1 + MCQ_2 + MCQ_3 + MCQ_4 + MCQ_5 + MCQ_6 + H + C + F + L + P + R 
H =~ MCQ_7 + MCQ_8 + MCQ_9 + MCQ_10 
C =~ MCQ_11 + MCQ_12 + MCQ_13 + MCQ_14 
F =~ MCQ_15 + MCQ_16 + MCQ_17 + MCQ_18 
L =~ MCQ_19 + MCQ_20 + MCQ_21 + MCQ_22 
P =~ MCQ_23 + MCQ_24 + MCQ_25 + MCQ_26 
R =~ MCQ_27 + MCQ_28 + MCQ_29 + MCQ_30 
RC =~ MCQ_2 + MCQ_7 + MCQ_14 + MCQ_17 + MCQ_20 + MCQ_25 + MCQ_28
'
American.fit <- cfa(model = overall.model,
                   data = MCQ[MCQ$country == "American",],
                   meanstructure = TRUE)

summary(American.fit,
        standardized = T,
        rsquare = T,
        fit.measures = T)


table_fit[2,] <- c("American Model", round(fitmeasures(American.fit,c("chisq","df","cfi","rmsea","srmr")),3))
kable(table_fit)

semPaths(American.fit,
         whatLabels = "std",
         edge.label.cex = 1,
         layout = "tree")
```


```{r}
#Chinese sample alone
Chinese.model <- '
GM =~ MCQ_1 + MCQ_2 + MCQ_3 + MCQ_4 + MCQ_5 + MCQ_6 + H + C + F + L + P + R 
H =~ MCQ_7 + MCQ_8 + MCQ_9 + MCQ_10 
C =~ MCQ_11 + MCQ_12 + MCQ_13 + MCQ_14 
F =~ MCQ_15 + MCQ_16 + MCQ_17 + MCQ_18 
L =~ MCQ_19 + MCQ_20 + MCQ_21 + MCQ_22 
P =~ MCQ_23 + MCQ_24 + MCQ_25 + MCQ_26 
R =~ MCQ_27 + MCQ_28 + MCQ_29 + MCQ_30 
RC =~ MCQ_2 + MCQ_7 + MCQ_14 + MCQ_17 + MCQ_20 + MCQ_25 + MCQ_28
'
Chinese.fit <- cfa(model = Chinese.model,
                   data = MCQ[MCQ$country == "Chinese",],
                   meanstructure = TRUE)

summary(Chinese.fit,
        standardized = T,
        rsquare = T,
        fit.measures = T)


table_fit[3,] <- c("Chinese Model", round(fitmeasures(Chinese.fit,c("chisq","df","cfi","rmsea","srmr")),3))
kable(table_fit)

semPaths(Chinese.fit,
         whatLabels = "std",
         edge.label.cex = 1,
         layout = "tree")
```


```{r}
#Configural invariance
configural.model <- '
GM =~ MCQ_1 + MCQ_2 + MCQ_3 + MCQ_4 + MCQ_5 + MCQ_6 + H + C + F + L + P + R 
H =~ MCQ_7 + MCQ_8 + MCQ_9 + MCQ_10 
C =~ MCQ_11 + MCQ_12 + MCQ_13 + MCQ_14 
F =~ MCQ_15 + MCQ_16 + MCQ_17 + MCQ_18 
L =~ MCQ_19 + MCQ_20 + MCQ_21 + MCQ_22 
P =~ MCQ_23 + MCQ_24 + MCQ_25 + MCQ_26 
R =~ MCQ_27 + MCQ_28 + MCQ_29 + MCQ_30 
RC =~ MCQ_2 + MCQ_7 + MCQ_14 + MCQ_17 + MCQ_20 + MCQ_25 + MCQ_28
'
configural.fit <- cfa(model = configural.model,
                   data = MCQ,
                   meanstructure = TRUE,
                   group = "country")

summary(configural.fit,
        standardized = T,
        rsquare = T,
        fit.measures = T)


table_fit[4,] <- c("configural Model", round(fitmeasures(configural.fit,c("chisq","df","cfi","rmsea","srmr")),3))
kable(table_fit)
```


```{r}
#metric invariance
metric.model <- '
GM =~ MCQ_1 + MCQ_2 + MCQ_3 + MCQ_4 + MCQ_5 + MCQ_6 + H + C + F + L + P + R 
H =~ MCQ_7 + MCQ_8 + MCQ_9 + MCQ_10 
C =~ MCQ_11 + MCQ_12 + MCQ_13 + MCQ_14 
F =~ MCQ_15 + MCQ_16 + MCQ_17 + MCQ_18 
L =~ MCQ_19 + MCQ_20 + MCQ_21 + MCQ_22 
P =~ MCQ_23 + MCQ_24 + MCQ_25 + MCQ_26 
R =~ MCQ_27 + MCQ_28 + MCQ_29 + MCQ_30 
RC =~ MCQ_2 + MCQ_7 + MCQ_14 + MCQ_17 + MCQ_20 + MCQ_25 + MCQ_28
'
metric.fit <- cfa(model = metric.model,
                   data = MCQ,
                   meanstructure = TRUE,
                   group = "country",
                   group.equal = c("loadings"))

summary(metric.fit,
        standardized = T,
        rsquare = T,
        fit.measures = T)


table_fit[5,] <- c("metric Model", round(fitmeasures(metric.fit,c("chisq","df","cfi","rmsea","srmr")),3))
kable(table_fit)
```


```{r}
#scalar invariance
scalar.model <- '
GM =~ MCQ_1 + MCQ_2 + MCQ_3 + MCQ_4 + MCQ_5 + MCQ_6 + H + C + F + L + P + R 
H =~ MCQ_7 + MCQ_8 + MCQ_9 + MCQ_10 
C =~ MCQ_11 + MCQ_12 + MCQ_13 + MCQ_14 
F =~ MCQ_15 + MCQ_16 + MCQ_17 + MCQ_18 
L =~ MCQ_19 + MCQ_20 + MCQ_21 + MCQ_22 
P =~ MCQ_23 + MCQ_24 + MCQ_25 + MCQ_26 
R =~ MCQ_27 + MCQ_28 + MCQ_29 + MCQ_30 
RC =~ MCQ_2 + MCQ_7 + MCQ_14 + MCQ_17 + MCQ_20 + MCQ_25 + MCQ_28
'
scalar.fit <- cfa(model = scalar.model,
                   data = MCQ,
                   meanstructure = TRUE,
                   group = "country",
                   group.equal = c("loadings","intercepts"))

summary(scalar.fit,
        standardized = T,
        rsquare = T,
        fit.measures = T)

table_fit[6,] <- c("scalar Model", round(fitmeasures(scalar.fit,c("chisq","df","cfi","rmsea","srmr")),3))
kable(table_fit)
```


```{r}
#strict invariance
strict.model <- '
GM =~ MCQ_1 + MCQ_2 + MCQ_3 + MCQ_4 + MCQ_5 + MCQ_6 + H + C + F + L + P + R 
H =~ MCQ_7 + MCQ_8 + MCQ_9 + MCQ_10 
C =~ MCQ_11 + MCQ_12 + MCQ_13 + MCQ_14 
F =~ MCQ_15 + MCQ_16 + MCQ_17 + MCQ_18 
L =~ MCQ_19 + MCQ_20 + MCQ_21 + MCQ_22 
P =~ MCQ_23 + MCQ_24 + MCQ_25 + MCQ_26 
R =~ MCQ_27 + MCQ_28 + MCQ_29 + MCQ_30 
RC =~ MCQ_2 + MCQ_7 + MCQ_14 + MCQ_17 + MCQ_20 + MCQ_25 + MCQ_28
'
strict.fit <- cfa(model = strict.model,
                   data = MCQ,
                   meanstructure = TRUE,
                   group = "country",
                   group.equal = c("loadings","intercepts","residuals"))

summary(strict.fit,
        standardized = T,
        rsquare = T,
        fit.measures = T)

table_fit[7,] <- c("strict Model", round(fitmeasures(strict.fit,c("chisq","df","cfi","rmsea","srmr")),3))
kable(table_fit)
```


```{r}
#predicted scores
predicted_scores <- lavPredict(strict.fit, type = "ov")


predicted_scores <- as.data.frame(do.call(rbind,predicted_scores))
predicted_scores$country <- c(rep("Chinese", nrow(MCQ_CN)), rep("American",nrow(MCQ_US)))

predicted_scores$sum <- apply(predicted_scores[,1:4],1,sum)

tapply(predicted_scores$sum,predicted_scores$country,mean)

```


```{r}

#effect size
Mean <- tapply(predicted_scores$sum,predicted_scores$country,mean)
SD <- tapply(predicted_scores$sum,predicted_scores$country,sd)
N <- tapply(predicted_scores$sum,predicted_scores$country,length)

effect_size <- d.ind.t(Mean[1],Mean[2],SD[1],SD[2],N[1],N[2], a = .05)
effect_size$estimate # give cohen's d
effect_size$statistic # t-test result comparing effect size
```
