---
title: "Portfolios 8"
author: "Qilin Zhang"
date: "2023-04-20"
output: html_document
---

###Bootscraping and simulation

This is an example of using data simulation and bootstrapping to validate the results from traditional statistical tests such as t-test and chi-square. In this attempt, I used data from the Openintro package called ncbirths. This data set contains the birth record data released by NC state in 2004. 

This exercise is derived from a exercise I did in the lab 11 of [Data Science for Psychologists](https://datascience4psych.github.io/DataScience4Psych/lab11.html).


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
```

### Load packages and data

```{r load-packages, message=FALSE}
library(ggplot2)
library(tidymodels)
library(openintro)
library(psych)
library(skimr)
library(boot)
library(tidyverse)
```

### descriptive 

I see 13 variables in total. There are 6 numeric variables and 7 categorical variables. 
```{r check}
data(ncbirths)

describe(ncbirths)
skim(ncbirths)

# visualization

ncbirths %>%
  ggplot(aes(x=weight))+
  geom_density() #baby weight

ncbirths %>%
  ggplot(aes(x=gained))+
  geom_density() #weight gained by mother during pregnancy in pounds

ncbirths %>%
  ggplot(aes(x=visits))+
  geom_density() #number of hospital visits during pregnancy

ncbirths %>%
  ggplot(aes(x=weeks))+
  geom_density() #length of pregnancy in weeks
```


### t-test bootstrap

It seems like there is only a few means lower than 7.250462 in the bootstrapping sample. After accounting for the proportion of the means lower than 7.25, the p value with 15000 rep of bootstraping is 0.0005. As a result, we can conclude that the mean of child's weight is significantly lower than those in 1995.

```{r white_baby}
ncbirths_white <- ncbirths %>%
  filter(whitemom == "white")

mean(ncbirths_white$weight) # sample mean = 7.25

#bootstrap
set.seed(123)
boot_bir_white <- ncbirths_white %>%
  # specify the variable of interest
  specify(response = weight) %>%
  # generate 15000 bootstrap samples
  generate(reps = 15000, type = "bootstrap") %>%
  # calculate the mean of each bootstrap sample 
  calculate(stat = "mean")

boot_bir_white %>%
  summarize(lower = quantile(stat, 0.025),
            mean = mean(stat),
            upper = quantile(stat, 0.975))

boot_bir_white$stat <- boot_bir_white$stat - (mean(ncbirths_white$weight) - 7.43) #7.43 was the mean baby weight in 1995
mean(boot_bir_white$stat)

boot_bir_white %>%
  summarize(lower = quantile(stat, 0.025),
            mean = mean(stat),
            upper = quantile(stat, 0.975))

boot_bir_white %>%
  filter(stat <= 7.250462) %>%
  nrow()/nrow(boot_bir_white)# p value = 0.0005


#visual
boot_bir_white %>%
  ggplot(aes(x=stat)) + 
  geom_histogram(binwidth = 0.001)+
  geom_vline(xintercept = 7.33)+ #lower quantile
  geom_vline(xintercept = 7.53)+ #higher quantile
  geom_vline(xintercept = 7.250462, color = "red")+
  geom_text(aes(x = 7.275, y = 100, label = "current mean"), color = "red", size = 3)+
  labs(title = "distribution for bootstrap means")
  

```

###t-test replication

Just want to confirm it with the traditional approach. Indeed, one sample t-test suggests that the mean of child's weight is significantly (based on p<0.05)lower than those in 1995.
```{r hypo_test}
t.test(x= ncbirths_white$weight,mu = 7.43)
```

###box plot comparison

From the plots, it seems like the baby weight of non-smokers are higher than smokers. 
```{r boxplot}
ncbirths_habitgiven <- ncbirths %>%
  filter(habit != "NA")

ncbirths_habitgiven %>%
  ggplot(aes(x=habit, y = weight, color = habit)) + 
  geom_boxplot()

```


###t-test bootstrap

Null hypothesis: There is no difference between baby weight with smoking and non-smoking parents among the population.
Alternative hypothesis: There is difference between baby weight with smoking and non-smoking parents among the population.

```{r}
ncbirths_habitgiven %>%
  group_by(habit) %>%
  summarise(mean_weight = mean(weight),
            median_weight = median(weight))

```


There is difference between baby weight with smoking and non-smoking parents among the population. In particular, the baby weight with smoking parents are significantly lower than those of the non-smoking parents. The confident interval represents that we have 95% of confident that the results t value will land between 0.45-4.16. 

```{r t-test_boot}

Smokers <- ncbirths_habitgiven %>%
  filter(habit=="smoker") %>%
  select(weight)
Smokers$id <- c(1:nrow(Smokers))

nonsmokers <- ncbirths_habitgiven %>%
  filter(habit=="nonsmoker") %>%
  select(weight)
nonsmokers$id <- c(1:nrow(nonsmokers))
smoking_boot <- merge(nonsmokers,Smokers,
                      by = "id",
                      all = T) %>%
  select(!id)

tstat <- function(data, indices) {
  sampled_data <- data[indices, ]
  t.test(sampled_data$weight.x, sampled_data$weight.y)$statistic
}

set.seed(1234)
boot_result <- boot(smoking_boot, tstat, R=15000)

mean(boot_result$t)

#confident interval
quantile(boot_result$t,0.025)
quantile(boot_result$t,0.975)

# transfer t to p
t_to_p <- function(t, df) {
  p <- 2 * pt(abs(t), df = df, lower.tail = FALSE)
  return(p)
}
t_to_p(mean(boot_result$t) ,999-2)

#replicate with traditional t-test
t.test(smoking_boot$weight.x,smoking_boot$weight.y)

```



###visualize cutoff

It looks like cutoff is at 34 to 35.

```{r cutoff}
cutoff <- ncbirths_habitgiven%>%
  filter(mature=="younger mom")%>%
  select(mage)%>%
  max()%>%
  as.numeric()
cutoff

ggplot(ncbirths_habitgiven, aes(x = mage, fill = mature))+
  geom_histogram(binwidth = 0.5)+
  geom_vline(xintercept = cutoff+0.5)
```

###chisqure

Null hypothesis:  the proportion of low birth weight babies is not different among mature or non-mature mothers
Alternative hypothesis:  the proportion of low birth weight babies is higher for mature mothers

It seems like there is no significant difference on the proportion of low birthweight babies between mature and non-mature mothers. Therefore, the original hypothesis in the question does not stand. 

```{r chisquare}

mature_lowweight <- ncbirths_habitgiven %>%
  select(c(mature,lowbirthweight)) %>%
  table()

mature_lowweight

#direct way
chisq.test(mature_lowweight,simulate.p.value = T,B = 10000)

chi_sq_stat <- function(data, indices) {
  tbl <- data[indices,]
  chisq <- chisq.test(tbl)$statistic
  return(chisq)
}

boot_results <- boot(data = mature_lowweight, statistic = chi_sq_stat, R = 10000)
# confident intervals
boot.ci(boot_results, type = "basic",conf = 0.95)

```